Parallel for Oregon Zip and WRF_Grid Intersection Proportion

### 2017-04-13 r_scripts/analysis/or_result_zip_manuscript.Rmd

```{r, eval = FALSE}
## 
# read locations of fires
fire_loc <- read_csv(paste0(smoke_path, "washington_fires_locations201209.csv"))

@@

method_list <- c('WRF-Chem Smoke', 'Geo-Weighted Smoke', 'Kriging Smoke')

@@

  i = 2
# dataframe to loop through
  df_to_loop <- data.frame(df_list[i])
  # indication of column
  outcome <- colnames(df_to_loop[76])
  # outcome name
  outcome_name <- outcome_list[i]

  # dataframe for analysis creation
  # bind columns back together 
  df_analysis <- df_to_loop %>%
    # only look at outcomes
    filter(outcome == 1) %>%
    # add another row that makes sure there is a person <15 in the dataframe
    # tricking xtabs to produce a 0 cell for the outcome for age <15
    add_row(outcome = 0, age_ind = 0)

  # cross tabs
  outcome_n <- xtabs(~ outcome, df_analysis)
  cross_tab_age <- xtabs(~ outcome + age_ind, df_analysis)
  cross_tab_sex <- xtabs(~ outcome + sex_ind, df_analysis)
  # empty matrix
  point_estimates <- matrix(nrow = 1, ncol = 7, byrow = T)

@@

# dataframe to loop through
  df_to_loop <- data.frame(df_list[i])
  # indication of column
  outcome <- colnames(df_to_loop[76])
  # outcome name
  outcome_name <- outcome_list[i]

  # extract covariates from dataframe
  covariates_df <- df_to_loop[, c(1:26, 71, 74, 76:85)]

  # extract pm values and divide by 10 and ordered
  which(colnames(df_to_loop)=="background_pm_zip") # code to find column numbers, 91
  pm_estimates_df <- df_to_loop[, c(88, 92:94)]/10  # create 10 unit increases

  # dataframe for analysis creation
  # bind columns back together 
  df_analysis <- cbind(covariates_df, pm_estimates_df) %>% 
    # remove missing pm values
    filter(!is.na(wrf_smk_pm_zip)) %>%

    # join in cdc met data
    # full_join(daily_zip_met, by = c("ZIPCODE", "date")) %>% 
    # the following code makes sure that the counterfactual values retained are 
    # symetric in that number of obs before = number of obs after
    mutate(obs_diff_admission = (fromdate - date)/7) 
    # dataframe is already for the entire fire season, so I don't need to subset anymore

@@

  # empty matrix
  point_estimates <- matrix(nrow = 3, ncol = 9, byrow = T)

@@

  # second loop to run a model for each pm estimation method
    for(j in 39:41){

@@

      # conditional logistic regression model
      mod <- clogit(outcome ~ df_analysis[[j]] + wrf_temp_zip + strata(personkey), df_analysis)

@@

      # populate matrix
      row_n <- j-38

@@

# subset columns I want to put in to the table
table_df <- combined_point_est_df %>% select(2, 3:7)

@@

# subset out global method
combined_point_est_df <- combined_point_est_df

@@

  print(print_plot)
  # save figure
  ggsave("./fig4.pdf", plot = print_plot, 
       width = 12, height = 8, units = "in")

@@

  xtabs(~ combined_point_est_df$outcome)
# subset out global method and respiratory outcomes ----
resp_point_est_df <- combined_point_est_df %>%

  filter(outcome == "All Respiratory" |
         outcome == "Asthma" |
         outcome == "COPD" |
         outcome == "Pneumonia" |
         outcome == "Acute Bronchitis" |
         outcome == "Broken Arm")

@@

# subset out global method and respiratory outcomes ----
cvd_point_est_df <- combined_point_est_df %>% 
   filter(outcome == "Cardiovascular Disease" |
         outcome == "Arrhythmia" |
         outcome == "Cerebrovascular Disease" |
         outcome == "Heart Failure" |
         outcome == "Ischemic Heart Disease" |
         outcome == "Myocardial Infarction")

>>>>

## ???
# read locations of fires
fire_loc <- read_csv(paste0(smoke_path, "washington_fires_locations201209.csv"))

@@

@@

  # dataframe for analysis creation
  # bind columns back together 
  df_analysis <- df_to_loop %>% select(c(1:16, 19, 27:28, 151:155)) %>% 
    # only look at outcomes
    filter(outcome == 1) %>%
    # left in only observations with estimates of smoke
    filter(!is.na(wrf_smk_pm_zip)) %>% 
    # limit to emergency or urgent care
    filter(ADM_TYPE == 1 | ADM_TYPE == 2) %>% 
    # add another row that makes sure there is a person <15 in the dataframe
    # tricking xtabs to produce a 0 cell for the outcome for age <15
    add_row(outcome = 0, age_cat = 0)

  # cross tabs
  outcome_n <- xtabs(~ outcome, df_analysis)
  cross_tab_age <- xtabs(~ outcome + age_cat, df_analysis)
  cross_tab_sex <- xtabs(~ outcome + sex_num, df_analysis)
  # empty matrix
  point_estimates <- matrix(nrow = 1, ncol = 7, byrow = T)

@@

  # dataframe for analysis creation
  # bind columns back together 
  df_analysis <- cbind(covariates_df, pm_estimates_df) %>% 
    # remove missing pm values
    filter(!is.na(wrf_smk_pm_zip)) %>% 
    # join in cdc met data
    full_join(daily_zip_met, by = c("ZIPCODE", "date")) %>% 
    # limit to emergency or urgent care
    filter(ADM_TYPE == 1 | ADM_TYPE == 2) %>%
    # the following code makes sure that the counterfactual values retained are 
    # symetric in that number of obs before = number of obs after
    mutate(obs_diff_admission = (date - date_admit)/7) 
    # dataframe is already for the entire fire season, so I don't need to subset anymore

@@

  # empty matrix
  point_estimates <- matrix(nrow = 4, ncol = 9, byrow = T)

@@

@@

      # conditional logistic regression model
      mod <- clogit(outcome ~ df_analysis[[j]] + daily_meanRH + daily_meanT + daily_meanWS + 
                      daily_meanPrcp + strata(PATIENTID), df_analysis)

@@

      # populate matrix
      row_n <- j-25

@@

# subset columns I want to put in to the table
table_df <- combined_point_est_df %>% select(2, 3:7) %>% 
  # exclude global smoke
  filter(pm_method != "Global Smoke")

@@

# subset out global method
combined_point_est_df <- combined_point_est_df %>% 
  filter(pm_method != "Global Smoke")

@@

  print(print_plot)
  # save figure
  ggsave("./fig3.pdf", plot = print_plot, 
       width = 12, height = 8, units = "in")

@@

  xtabs(~ combined_point_est_df$outcome)
# subset out global method and respiratory outcomes ----
resp_point_est_df <- combined_point_est_df %>% 
  filter(pm_method != "Global Smoke") %>% 
  filter(outcome == "All Respiratory" |
         outcome == "Asthma" |
         outcome == "COPD" |
         outcome == "Pneumonia" |
         outcome == "Acute Bronchitis" |
         outcome == "Broken Arm")

@@

# subset out global method and respiratory outcomes ----
cvd_point_est_df <- combined_point_est_df %>% 
  filter(pm_method != "Global Smoke") %>% 
  filter(outcome == "Cardiovascular Disease" |
         outcome == "Arrhythmia" |
         outcome == "Cerebrovascular Disease" |
         outcome == "Heart Failure" |
         outcome == "Ischemic Heart Disease" |
         outcome == "Myocardial Infarction")

### 2017-04-13 r_scripts/parallel_presentation.Rmd

```{r parallel set, eval = FALSE}
# Setup for parallel computing before for loop ---------------------------------
cores <- detectCores() # 48
cl <- makeCluster(cores) # use half the cores on the vet cluster
registerDoParallel(cl)
# load packages on each cluster
clusterCall(cl, function() library(rgdal))
clusterCall(cl, function() library(sp))
clusterCall(cl, function() library(rgeos))

>>>>

```{r parallel, eval = FALSE}
# Setup for parallel computing before for loop ---------------------------------
cores <- detectCores() # 48
cl <- makeCluster(cores) # use half the cores on the vet cluster
registerDoParallel(cl)
# load packages on each cluster
clusterCall(cl, function() library(rgdal))
clusterCall(cl, function() library(sp))
clusterCall(cl, function() library(rgeos))
